Predictability of Crash Modelling From the Data with Improved Quality Using Level Sets Surveillance System

### 2017-12-07 draft.Rmd
Add files via upload

##Level set setting
$\gamma_X(\alpha) = \underset{n}{\operatorname{sup}}\{X:\frac{\|C_X(n)\|}{N} \le \alpha\}$, where $n$ is the number of Logmile segments needed to satisfy the condition.

>>>>

##Level sets

$\gamma_X(\alpha) = \underset{n}{\operatorname{sup}}\{X:\frac{\|C_X(n)\|}{N} \le \alpha\}$, where $n$ is the number of Logmile segments needed to satisfy the condition.
